---
title: "Solar panel collection data"
author: "Ethan Meersman"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(Hmisc)

```

### Below is the code to create a dataset about solar panels and energy collection and basic analysis of the variables.


```{r}

# Set the seed for reproducibility
set.seed(20230130)

# Generate random data for solar panels
n <- 1000 # number of observations
panel_area <- runif(n, min = 5, max = 20) # area of solar panels in m^2
panel_efficiency <- runif(n, min = 0.1, max = 0.2) # efficiency of solar panels
panel_orientation <- sample(c("north", "south", "east", "west"), n, replace = TRUE) # orientation of solar panels
sunlight_hours <- rnorm(n, mean = 6, sd = 1.5) # average hours of sunlight per day
panel_age <- rnorm(n, mean = 3, sd = 1) # age of the solar panel installation
energy_output <- panel_area * panel_efficiency * (sunlight_hours/24) * (1 - panel_age/10) + rnorm(n, mean = 0, sd = 10) # energy output of the solar panels

# Combine the variables into a data frame
solar_data <- data.frame(panel_area, panel_efficiency, panel_orientation, sunlight_hours, panel_age, energy_output)

```


```{r}

summary(solar_data)

describe(solar_data)

write.csv(solar_data, file = "meersman_solar_data.csv", row.names = FALSE)

```

# Data Dictionary

panel_area: the area of the solar panels in square meters.

panel_efficiency: the efficiency of the solar panels.

panel_orientation: the orientation of the solar panels (north, south, east, or west).

sunlight_hours: the average number of hours of sunlight per day.
panel_age: the age of the solar panel installation.

energy_output: the energy output of the solar panels.
